---
title: "drakeme"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{drakeme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# `drakeme()`: Quickly jump into a drake workflow

``` r
flowme::drakeme()
```

`flowme::drakeme()` includes our boilerplate code for `drake`-powered projects 
in your current session. It is originally based on McBain's
[`dflow`](https://github.com/MilesMcBain/dflow) and it is tailored to our
report-generating projects.

## Aims of this boilerplate

We put together this template, mainly, to:

- **A1**: Make it easy to jump into a drake workflow. In particular, for those 
  used to the analysis as R package approach.
- **A2**: Make it easy and one-sight-clear what the project is all about. 
  In particular, for a new person collaborating or overtaking the project 
  (which, of course, may well be future you).
- **A3**: Cover the most common use case we have, which is a data analysis 
  project that ends up in a somewhat beefy report (as opposed to, for example, 
  a ML project that ends up putting a model up in "production").

## Features to achieve those aims

These are the key features to achieve those aims (admittedly, some 
could be highly controversial. Yet, they work for us).

- **Fully functional `drake` project at the push of a button**: once installed, 
  `flowme` helps you setup a drake project with one-function call 
  (`flowme::drakeme()`), including all required packages.
  It will get you started with a "hello world" project that you can actually 
  run (`drake::r_make()`) and see the output. **A1**

- **`devtools::load_all()` friendly**: `flowme::drakeme()` makes sure your 
  project has a DESCRIPTION file, and if you have `devtools` installed,
  `devtools::load_all()` would just work (you may need to restart RStudio for
  the keyboard shortcut to work). By placing `0_packages.R` within R directory,
  packages will also be loaded/attached.
  
- **A `bookdown`-based report/book in the flow**: `flowme::drakeme()` sets the
  stage for the project to produce a report with `bookdown`. You simply add
  `Rmd` files to the "report" folder and you are good to go. This is achieved by 
  including a target at the end of the plan to render all `Rmd` files in the 
  `report` directory into a single book. Thus, you do not have to include one 
  target for each `Rmd`, but rather just work on your `Rmd` and put them all 
  in the `report` directory. Take a look at `plan_bookme()` and `bookme()` to 
  see how this is done.

Here's the file structure `flowme::drakeme()` includes in your current project:

```{r include=FALSE}
example_dir <- fs::dir_create(paste0(tempdir(), "/drake_example"))
xfun::in_dir(example_dir, flowme::use_drake())
```

``` r
```{r echo=FALSE, results='asis'}
xfun::in_dir(example_dir, fs::dir_tree(all = TRUE))
```
```



## Workflow notes

- The big picture plan (`the_plan`) should be defined in `_drake.R`,
  by binding together sub-plans. So no details on the processing here (unless
  it is a really simple project, in which case you probably do not need `drake` 
  anyway, so, please just don't). Hence, the plan should look something like 
  the example below, which makes it easy for a newcomer to quickly know what 
  the project is all about.
  
  ``` r
  the_plan <- drake::bind_plans(
  
    plan_network_analysis(),
    plan_survey_analysis(),
    plan_financial_analysis(),
    plan_bookme() # Just render the report using bookdown
  )
  ```
  
- Define sub-plans within functions that return a `drake::drake_plan`. 
  Defining the plans within functions instead of directly as objects helps 
  navigating the project. You look at the plan, put the cursor on the sub-plan 
  you want to go to and hit F2.
  
- Include `Rmd` in the `report` directory, using the targets in the plans by 
  calling `drake::loadd` or `drake::readd`
