---
title: "flowme"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flowme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# `drakeme()`

``` r
flowme::drakeme()
```

`flowme::drakeme()` includes our boilerplate for `drake`-powered projects in 
your current session. It is based on McBain's [`dflow`](https://github.com/MilesMcBain/dflow)
and it is tailored to our report-generating projects.

Basically it includes a couple of convenience features as follows:

- Sets the stage for the project to produce a report with `bookdown`. 
  Simply add .Rmd files to the "report" folder and you are good to go.
- Proposes a one-plan-per-chapter approach (defining the plans within functions 
  to help code navigation).
- A couple of wrappers for `drake` functions to better fit our needs.

It works by creating the following file structure in your current project:

```{r echo=FALSE, results='hold'}
xfun::in_dir(fs::path_package("flowme", "templates/drake/"), fs::dir_tree())
```

## Workflow notes

- The big picture plan (`the_plan`) should be defined in `_drake.R`
  by binding together sub-plans. So no details on the processing here (unless
  it is a really simple project, in which case you probably do not need `drake` 
  anyway, so, ..., just don't). Hence, the plan should look something like this, 
  which makes it easy for a newcomer to quickly know what the project is all 
  about.
  
  ``` r
  the_plan <- drake::bind_plans(
  
    plan_network_analysis(),
    plan_survey_analysis(),
    plan_financial_analysis(),
    plan_bookme() # Just render the report using bookdown
  )
  ```
  
- Define sub-plans within functions that return a `drake::drake_plan`. 
  Defining the plans within functions instead of directly as objects helps 
  navigating the project. You look at the plan, put the cursor on the sub-plan 
  you want to go to and hit F2.
  
- Include .Rmd in the `report` directory, using the targets in the plans by 
  calling `drake::loadd` or `drake::readd`

