---
title: "flowme"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flowme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# `drakeme()`

``` r
flowme::drakeme()
```

`flowme::drakeme()` includes our boilerplate for `drake`-powered projects in 
your current session. It is based on McBain's [`dflow`](https://github.com/MilesMcBain/dflow)
and it is tailored to our report-generating projects.

Basically it includes a couple of convenience features as follows:

- Sets the stage for the project to produce a report with `bookdown`. 
  Simply add .Rmd files to the "report" folder and you are good to go.
- Proposes a one-plan-per-chapter approach (defining the plans within functions 
  to help code navigation).
- A couple of wrappers for `drake` functions to better fit our needs.

It works by creating the following file structure in your current project:

```{r echo=FALSE, results='hold'}
xfun::in_dir(fs::path_package("flowme", "templates/drake/"), fs::dir_tree())
```

