---
title: "targetsme"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{targetsme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# We are transitioning to {targets} ...

So, we now include a bare-bones {targets} project template that you can use
using `flowme::targetsme()` or `flowme::use_targets()`, which includes
the following files in your current project:

```{r include=FALSE}
#example_dir <- fs::dir_create(paste0(tempdir(), "/targets_example"))
#xfun::in_dir(example_dir, flowme::use_targets())
```

``` r
```{r echo=FALSE, results='asis'}
#xfun::in_dir(example_dir, fs::dir_tree(all = TRUE))
```
```

The aims are similar to those of our {drake} template (see `vignette("drakeme",
package = "flowme")`). But currently our {targets} template is very thin. It
only includes:

- Fully functional `{targets}` project at the push of a button: once installed, 
  `flowme` helps you setup a project
  (`flowme::targetsme()`) that you can actually 
  run (`targets::tar_make()`) and see the output.

- Prepares the environment in `.Rprofile` and leaves `_targets.R` script
  only to define your pipeline. (we are not convinced yet on this approach, 
  but let's see how it goes)

- Includes a `bookdown`-based report/book in the pipeline, now using a target
  factory in `flowme::tar_bookdown()`. Again, you simply add
  `Rmd` files to the "report" folder and you are good to go. 
  
- Again, the big picture plan should be defined in `_targets.R`,
  by binding together sub-plans. Here we still prefer drake-like syntax 
  and therefore we will use `tarchetypes::tar_plan` within functions to help
  navigating the project.

